---
title: "Assignment_2"
author: "Dan Boguslavsky"
date: "5/12/2020"
output: html_document
---
```{r}
rm(list=ls())
```

```{r Question 1}
#install.packages('rattle.data')
library('rattle.data')
wine<-rattle.data::wine
?wine
```

#1.a.
```{r Q-1,a}
plot(Flavanoids~Phenols,data = wine)
```
It seems that indeed, Flavanoids and Phenols have some linear relationship between them.

#1.b.
```{r Q-1,b}
```
The model: Flavanoids = β0 + β1*Phenols + error
in this model we assuming that the amount of Flavanoids affected by the amount of Phenols.
Additionaly we assuming all of the basic assumption of the linear regretion.


#1.c.
We want to minimize the sum of residual squares. So to get those expressions we need to deriviate the sum by β0 and β1 and equal to '0',
and then solve the equations, and find β0 and β1.

There are few assumptions we must assume to make those calculations:
1. Independence - we assume that the residuals are independent.
2. Centered - we assume that the Expected value of the resudials is '0'. (E(res) = 0).
3. Normality - we assume that the resudials are
1. The relation between 'Flavanoids'  and 'Phenols' is linear.
2. 'Flavanoids' ~ N(µ,)

#1.d.
```{r Q-1,d}
lm.Flavanoids.Phenols<- lm(wine$Flavanoids~wine$Phenols)
#Estimation resaults:
predict(lm.Flavanoids.Phenols)
#Plot + regression line:
plot(Flavanoids~Phenols,data = wine)
abline(coef(lm.Flavanoids.Phenols)[1:2])
```

#1.e.
```{r Q-1,e}
#Slope coefficient:
coef(lm.Flavanoids.Phenols)[2:2]
summary(lm.Flavanoids.Phenols)
```
The sope coefficient is significant. Be base it on the t-value of the effect - which is 22.82.
That indicates a very significant effect. We can also be assisted by the "star" code on the left of the "summary" command - "***" means significance level of under 0.001% for the effect to be insignificant.

#1.f.
```{r Q-1,f}
plot(density(lm.Flavanoids.Phenols$residuals),main = "Residuals",col="red")
legend("topright", legend=c("syntatic norm dist", "residual dist"),
           col=c("black","red"),lty=1, cex=0.7)
set.seed(256)             
lines(density(rnorm(1:178,0,0.5)))
shapiro.test(lm.Flavanoids.Phenols$residuals)
```

We add normal distrabiotion line to compare it with the residual distrecution.
Additionaly we add shapiro-wilk test in order to verifay the segnigicant the residual distrecution is normal distrebiotion.
You can noticte the simularity in the plot and the p-value of the shapiro-wilk test is 0.0003786 (very segnigicant).

#1.h.
```{r Q-1,h}
library("ggplot2")
ggplot(wine, aes(x=Flavanoids, y=Phenols, color=Type)) + geom_point() + 
```


#1.i.
```{r Q-1,i}
type_1 <- subset(wine,Type==1)
type_2 <- subset(wine,Type==2)
type_3 <- subset(wine,Type==3)
lm_type_1 <- lm(type_1$Flavanoids ~ type_1$Phenols)
lm_type_2 <- lm(type_2$Flavanoids ~ type_2$Phenols)
lm_type_3 <- lm(type_3$Flavanoids ~ type_3$Phenols)
ggplot(wine, aes(x=Phenols, y=Flavanoids, color = Type)) + geom_point() + geom_smooth(method = lm, se = FALSE)
```


```{r Q-1,i}
coef(lm_type_1)
coef(lm_type_2)
coef(lm_type_3)
```










#2.b.
```{r Q-2, b}
library("ggplot2")
lm_dif_sl_co <-lm(mpg ~ as.factor(cyl)*hp, data = mtcars)
ggplot(mtcars, aes(x=hp, y=mpg, color=as.factor(cyl))) + geom_point() + geom_smooth(method = lm, se = FALSE)
summary(lm_dif_sl_co)
qqnorm(lm_dif_sl_co$residuals); qqline(lm_dif_sl_co$residuals)
```
```{r}
lm_dif_co <-lm(mpg ~ as.factor(cyl) + hp, data = mtcars)
summary(lm_dif_co)
equation1 = function(x){coef(lm_dif_co)[4]*x+coef(lm_dif_co)[1]}
equation2 = function(x){coef(lm_dif_co)[4]*x+coef(a)[1]+coef(lm_dif_co)[2]}
equation3 = function(x){coef(lm_dif_co)[4]*x+coef(a)[1]+coef(lm_dif_co)[3]}
library("ggplot2")
ggplot(mtcars, aes(x=hp, y=mpg, color=as.factor(cyl))) + geom_point() + stat_function(fun=equation1,geom="line",color=scales::hue_pal()(2)[1]) + stat_function(fun=equation2,geom="line",color=scales::hue_pal()(2)[2]) + stat_function(fun=equation3,geom="line",color=scales::hue_pal()(2)[3])
qqnorm(lm_dif_co$residuals); qqline(lm_dif_co$residuals)
```
```{r}
library("ggplot2")
lm_same <- lm(mpg ~ hp, data = mtcars)
ggplot(mtcars, aes(x=hp, y=mpg)) + geom_point() + geom_smooth(method = lm, se = FALSE)
summary(lm_same)
qqnorm(lm_same$residuals); qqline(lm_same$residuals)
```

```{r}
anova(lm_dif_sl_co,lm_dif_co, test='F')
```



#2.c.
```{r Q-2, c}
mt_db <- as.data.table(mtcars)
auto_db <- mt_db[mt_db$am==0]
auto_db$eng <- ifelse (auto_db$vs==0, " v-shaped", " straight")
summary(lm(wt~eng , data = auto_db))
#auto_db$vs <- as.factor(auto_db$vs)
#plot(wt~as.factor(eng), data = auto_db)
#lm_auto_vs <-lm(wt~vs, data = auto_db)
#summary(lm_auto_vs)
#ggplot(auto_db, aes(x=as.factor(eng), y=wt)) + geom_point() + geom_smooth(method = lm, se = FALSE)
#qqnorm(lm_auto_vs$residuals); qqline(lm_auto_vs$residuals)
```






#3.a.
```{r}
wine_db <- wine
wine_db$is_1 <- ifelse(wine_db$Type==1, 1, 0)
step(glm(is_1~., data = wine_db, family = binomial))
```


#3.b.
```{r}
abc<-function(x){print(5)}
```

git test






